\textbf{ Spectrophotometric parallaxes with \project{The Cygnet}:\\ Accurate distances for luminous red-giant stars }

### 2018-08-03 paper/sp.tex
sdssvv

If we want to make precise kinematic and element-abundance maps
of the Milky Way disk out to large heliocentric radii,
and especially through the extinction to the other side of the Galactic Center, we will
need to make use of luminous red giants, and we will need to observe in
the infrared.
These arguments motivate the \apogee\ (CITE), \apogee-2 (CITE), and \sdssv\ (CITE)
projects, which take spectra in the infrared, and deliver detailed abundances
along the entire red-giant branch up to the tip.
The maps made with these data will reveal the dynamics of the Milky Way and its disk,
and show us how and where stars form, and how they migrate around (and out of) the
disk with time.

@@

This work has made use of data from the European Space Agency (ESA) mission
\gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data
Processing and Analysis Consortium (\acronym{DPAC},
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the
\acronym{DPAC}
has been provided by national institutions, in particular the institutions
participating in the \gaia\ Multilateral Agreement.

@@

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Bailer-Jones et al.(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W 2018, arXiv:1804.07766 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\end{thebibliography}

>>>>

If we want to make precise kinematic and element-abundance maps
of the Milky Way disk out to large heliocentric radii,
and especially through the extinction to the other side of the Galactic Center, we will
need to make use of luminous red giants, and we will need to observe in
the infrared.
These arguments motivate the \apogee\ (CITE), \apogee-2 (CITE), and \sdssv\ (\citealt{sdssv})
projects, which take spectra in the infrared, and deliver detailed abundances
along the entire red-giant branch up to the tip.
The maps made with these data will reveal the dynamics of the Milky Way and its disk,
and show us how and where stars form, and how they migrate around (and out of) the
disk with time.

@@

This work has made use of data from the European Space Agency (\acronym{ESA}) mission
\gaia\ (\url{https://www.cosmos.esa.int/gaia}), processed by the \gaia\ Data
Processing and Analysis Consortium (\acronym{DPAC},
\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the
\acronym{DPAC}
has been provided by national institutions, in particular the institutions
participating in the \gaia\ Multilateral Agreement.

@@

\begin{thebibliography}{}
\bibitem[Abolfathi \etal(2018)]{dr14} Abolfathi, B., Aguado, D.~S., Aguilar, G., \etal\ 2018, \apjs, 235, 42 
\bibitem[Bailer-Jones et al.(2018)]{calj} Bailer-Jones, C.~A.~L., Rybizki, J., Fouesneau, M., Mantelet, G., \& Andrae, R.\ 2018, \aj, 156, 58 
\bibitem[Blanton \etal(2017)]{sdssiv} Blanton, M.~R., Bershady, M.~A., Abolfathi, B., \etal\ 2017, \aj, 154, 28 
\bibitem[Hogg(2018)]{gaialf} Hogg, D.~W 2018, arXiv:1804.07766 
\bibitem[Kollmeier \etal(2017)]{sdssv} Kollmeier, J.~A., Zasowski, G., Rix, H.-W., \etal\ 2017, arXiv:1711.03234 
\bibitem[Lindegren \etal(2018)]{lindegren} Lindegren, L., Hernandez, J., Bombrun, A., \etal\ 2018, arXiv:1804.09366 
\bibitem[Lutz \& Kelker(1973)]{lk} Lutz, T.~E., \& Kelker, D.~H.\ 1973, \pasp, 85, 573 
\bibitem[Skrutskie \etal(2006)]{zmass} Skrutskie, M.~F., Cutri, R.~M., Stiening, R., \etal\ 2006, \aj, 131, 1163 
\end{thebibliography}
